The fraction of polar aligned circumbinary disks

### 2024-12-29 src/tex/ms.tex
Add ref to disk shadow paper

Consider now a wave-like disk with inner radius $r_\text{in}$ and outer radius $r_\text{out}$. If $r_\text{out}$ is sufficiently large, then a break will occur at a radius $r_\text{break}$ that depends on the specific parameters of the disk \citep[see][eq. (9)]{rabago2024}. The two regions can be treated independently of each other. For the inner disk, the outer edge is sufficiently connected to the inner edge, and the whole region precesses together on a characteristic timescale $t_\text{p}(r_\text{in}) < t_\text{p} \lesssim t_\text{p}(r_\text{break})$. The outer disk may break again if $r_\text{out}$ is very large, but either way it will precess on its own characteristic timescale. We now have two independent rings, each with its own precession timescale. Due to the strong dependence of $t_\text{p}$ on $r$, the inner disk is much more likely to reach alignment in a disk lifetime, and the different alignment timescales means the disks will be misaligned from each other, potentially causing a shadow to be cast on the outer disk \citep[see][\TJ{and others}]{benisty2023,su2024,zhang2024}.

>>>>

Consider now a wave-like disk with inner radius $r_\text{in}$ and outer radius $r_\text{out}$. If $r_\text{out}$ is sufficiently large, then a break will occur at a radius $r_\text{break}$ that depends on the specific parameters of the disk \citep[see][eq. (9)]{rabago2024}. The two regions can be treated independently of each other. For the inner disk, the outer edge is sufficiently connected to the inner edge, and the whole region precesses together on a characteristic timescale $t_\text{p}(r_\text{in}) < t_\text{p} \lesssim t_\text{p}(r_\text{break})$. The outer disk may break again if $r_\text{out}$ is very large, but either way it will precess on its own characteristic timescale. We now have two independent rings, each with its own precession timescale. Due to the strong dependence of $t_\text{p}$ on $r$, the inner disk is much more likely to reach alignment in a disk lifetime, and the different alignment timescales means the disks will be misaligned from each other, potentially causing a shadow to be cast on the outer disk \citep[see][]{benisty2023,su2024,zhang2024,zhu2024}.
